Dotted Suffix Trees\\A Structure for Approximate Text Indexing

### 2005-09-03 paper/search.tex
Use \mathcal{O} for big-O Specify that reporting can be done in linear time

The recursive call at line~\ref{algoline:search:followDot} means that a dot link was followed. There are at most $O(m^k)$ places where a dot link can be followed while descending a string~\footnote{For $k=1$ each point in the string. For $k>1$, each path for $k-1$, can now have at most $m$ extra branches.}. Following one path in the tree takes $O(m)$ time. Therefore, the total time is $O(m^{k+1})$.

>>>>

The recursive call at line~\ref{algoline:search:followDot} means that a dot link was followed. There are at most $\mathcal{O}(m^k)$ places where a dot link can be followed while descending a string~\footnote{For $k=1$ each point in the string. For $k>1$, each path for $k-1$, can now have at most $m$ extra branches.}. Following one path in the tree takes $\mathcal{O}(m)$ time. Therefore, the total time is $\mathcal{O}(m^{k+1})$ without the reporting of occurences (which can be done in time linear to the number of occurences).
